\cvsection{Experience}

\begin{cventries}
  \cventry
    {Graduate Teaching Assistant (Part time)} % Job title
    {Texas A\&M University} % Organization
    {College Station, United States} % Location
    {Aug. 2021 - May. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lab instructor for ECEN 449 Microprocessor System Design (2022 Spring).}
        \item {Lab instructor for ECEN 350 Computer Organization and Design (2021 Fall).}
      \end{cvitems}
    }
    
  \cventry
    {Grader (Part time)} % Job title
    {Texas A\&M University} % Organization
    {College Station, United States} % Location
    {Aug. 2020 - Dec. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Grader for ECEN 350 Computer Organization and Design (2020 Fall).}
      \end{cvitems}
    }
    
  \cventry
    {TAMU Robomaster Robotics Advisor} % Job title
    {Texas A\&M University Robomaster Society} % Organization
    {College Station, United States} % Location
    {Aug. 2020 - Jun. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working with the embedded and the computer vision teams.}
        \item {Writing and debugging code in C/C++ for ARM cortex M4 processor.}
        \item {Advise on the control of the robots used for Global Robomaster Competition.}
      \end{cvitems}
    }

  \cventry
    {Student System Administrator (Part time)} % Job title
    {Imperial College Union} % Organization
    {London, United Kingdom} % Location
    {Nov. 2018 - Mar. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working with the Imperial College Union Administration Team.}
        \item {Configuring and maintaining WordPress websites for student clubs and societies at Imperial College London.}
      \end{cvitems}
    }

  \cventry
    {Software Engineering Intern (Full time)} % Job title
    {Fleetonomy} % Organization
    {Tel Aviv, Israel} % Location
    {Jul. 2018 - Sep. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing the testing interface as part of a Uber-like web application in Python, JavaScript and SQL.}
        \item {Worked on frontend, backend, unit test and database.}
        \item {Worked on integrating third-party monitoring services such as Datadog via API calls to the web application.}
      \end{cvitems}
    }
    
    \cventry
    {Learner} % Job title
    {Summer Academy of Code} % Organization
    {Oxford, United Kingdom} % Location
    {Sep. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Learning dynamic website developing and hosting.}
        \item {Developed an online accounting application using Node.js.}
      \end{cvitems}
    }
    
    \cventry
    {Competitor} % Job title
    {Piwars} % Organization
    {Cambridge, United Kingdom} % Location
    {Apr. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Robotics competition. Teamed up with BigSubhakrish Krishnamra, Haojun Zhang, Hang Su and Ruochen Zhao.}
        \item {Designed and built a functional remote-control car based on the Raspberry pi with sensors.}
      \end{cvitems}
    }
    
\end{cventries}
