\cvsection{Projects \& Research}

\begin{cventries}

    \cventry
    {}
    {Approximating Ideal Prefetches in L2 Cache}
    {}
    {}
    {
        \begin{cvitems}
            \item An iterative method that investigates the upper limit of ideal prefetching in L2 cache with realistic bandwidth constraints.
            \item Published on IEEE CAL. Aim for an IEEE ISCA publication.
        \end{cvitems}
    }

    \cventry
    {}
    {Context Switch Optimization}
    {}
    {}
    {
        \begin{cvitems}
            \item An approach to prime the micro-architectural states after context switches to reduce stalls due to cold cache states.            
            \item Aim for an IEEE CAL publication for comments. Then aim for an IEEE ISPASS publication as a full conference paper.
        \end{cvitems}
    }
    
    \cventry
    {}
    {Formal Verification for a Traffic System}
    {}
    {}
    {
        \begin{cvitems}
            \item Design and verify a traffic system with formal techniques.
            \item Traffic system implemented in Python flask with a web-page-based GUI.
            \item Verification done by re-coding the application in Promela and run using Spin, a verification tool for multi-threaded applications.
        \end{cvitems}
    }
    
    \cventry
    {} % Empty position
    {Undergraduate Final Year Project} % Project
    {} % Empty location
    {} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Graphical hardware description language (HDL) editor that outputs Verilog HDL code.}
        \item {Implemented in F\# and integrated with the Fable compiler to transpile F\# to JavaScript.}
        \item {Transpiled JavaScript code run under the Electron framework that supports Linux, MacOS and Windows.}
      \end{cvitems}
    }
    
    \cventry
    {} % Empty position
    {Using FPGA Hardware for Algorithm Acceleration} % Project
    {} % Empty location
    {} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Configure a FPGA device to run the NIOS II processor.}
        \item {Algorithm written in C and uploaded to the FPGA device and executed in the NOIS II processor.}
        \item {Explore ways to reduce execution time, including using pipeline, different types of multipliers, and the CORDIC algorithm.}
        \item {Implement hardware blocks to realize the CORDIC algorithm with pipeline.}
        \item {Results show the use of dedicated hardware reduces the execution time significantly with increase in hardware usage.}
      \end{cvitems}
    }
    
    \cventry
    {} % Empty position
    {Adding Features to Visual2, the Arm Assembly Simulator} % Project
    {} % Empty location
    {} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Add new features to Visual2, including pipelining display, multiplication instructions and improvement to the error messages.}
        \item {Code in F\# and JavaScript.}
      \end{cvitems}
    }
    
    \cventry
    {} % Empty position
    {Undergraduate Second Year Project} % Project
    {} % Empty location
    {} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Gloves with sensors built in to detect palm facing, acceleration and finger bending for sign language translation.}
        \item {Machine learning model training with readings from sensors.}
        \item {Sign language translation achieved by feeding sensor readings to machine learning models.}
      \end{cvitems}
    }

\end{cventries}